Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-25 Ben_Manuscripts/structure_paper/Draft.tex
Revisions and new figures

  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{One can only speculate about solute behavior inside the membrane
	  pores based on the previously established picture of the pore structure (a). 
      We use a detailed molecular model in order to appropriately model the pore's
      complex architecture which is crucial to understanding the mechanism of solute
	  transport (b). The head group region is colored blue and the tail region is
	  colored cyan in both representations. This image was generated from the molecular
	  simulations run for this paper.}~\label{fig:detail}
  \end{figure}

@@

  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
  systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
  have an equilibrated pore spacing c.a. 0.50 nm higher than experiment. Ordered basin systems
  built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.

@@

  \begin{figure}[htb]
  \centering
  \includegraphics[width=\textwidth]{box_dimensions.png}
  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5 \AA~$), the unit cell
  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
  constant across all cases. The y dimension box vectors are not included since we use 
  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
  \end{figure}

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
  \end{figure}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We extended each simulation by 100 ns in order to get more equilibrated 
  data. We generated simulated patterns using the extended of simulation trajectories
  The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

  %BJC5: put figure letters in upper left hand corner of each pattern.
  \begin{figure}[htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			        %\caption{Sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
	        		%\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
	        		%\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			        %\caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
			\end{subfigure}

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
  simulated patterns. They are also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
  maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

  The simulated XRD patterns of the parallel displaced configurations show an additional
  reflection due to their helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
  is characteristic of a helix (reference something).
  %BJC5: reference something like a dna diffraction paper
  It is possible that these reflections contribute to the continuation of R-double into R-
  alkanes, as seen in the experimental pattern.
  %BJC5: not sure above sentence is clear (or necessary to say)

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. Table 
  ~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1.
  % BJC5: show how intensities are measured in supporting info
  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
  significantly higher than experiment in our simulations. R-spots is measured as the average
  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
  inspection. If the spots were not easily discernable, then the intensity was taken as that of
  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
  cases. There is no R-double intensity to be measured. Figures are provided in 
  section S\ref{S-section:xrd_intensities} to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

  %BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
  to sample enough independent configurations. Increasing the number of trajectory frames
  used to simulate the structure factor within a given interval of time does not offer 
  any improvement.

@@

  \begin{figure}
	  \begin{subfigure}{0.45\linewidth}
	  	\centering
	  	\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
	  	\caption{}
	  \end{subfigure}
	  \begin{subfigure}{0.45\linewidth}
	  	\centering
	  	\includegraphics[width=\linewidth]{rzplot_layered_280K_jet.png}
	  	\caption{}\label{fig:sandwiched280K}
	  \end{subfigure}
  \caption{R-spots increases in intensity when the temperature of the system is lowered to 280K.
  In this case, the simulated R-spots is more intense than experiment.}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

  To understand the origin of R-spots, we determined which
  atoms gave rise to the feature. Since R-spots is present as higher intensity
  spots within R-alkanes, it is likely that the spots arise as a consequence of
  the tails. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
  the centroids of the tails (Figure S-\ref{S-fig:centroids}) and measured the angle
  between each centroid and its nearest neighbors with respect to the plane of the 
  membrane. We see distinct peaks in the distribution of these angles 
  (Figure~\ref{fig:tail_packing}).

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails}
  are located at $\pm 33 \degree$ which is the same location where the highest
  intensity of spots are located on the simulated patterns. We confirmed this 
  conclusion by radially integrating the 2D WAXS pattern for 
  $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe distinct peaks ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figure~\ref{fig:layered_integration}). We performed the same integration on
  the raw experimental data and found the angle at which R-spots reaches its
  highest intensity to be $\pm 37 \degree$ which is a reconcilable difference
  with our simulated results.

@@

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
	 	\vspace{-2em}
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
        tail-only trajectory still shows R-spots}\label{fig:tails}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{1D correlation functions of the center of masses of aromatic head groups, $g(z)$, show
  decaying oscillatory behavior. We calculated the correlation length by fitting a decaying exponential
  function (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The correlation length is
  longer for ordered basin systems (Table~\ref{table:correlation_length}).
  We did not attempt to calculate the correlation length for (d) because there are no clear peaks. We 
  assume that its correlation is less than the vertical distance between monomers.}\label{fig:correlation}
  \end{figure}

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \midrule
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.5 $\pm$ 0.4            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 15.5 $\pm$ 1.9           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $\mathit{d}_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
  \bottomrule
  \end{tabular}
  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
  \label{table:correlation_length}
  \end{table}

@@

  The correlation length between stacked monomer head groups of the ordered systems also show
  closer agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
  not extract a reliable correlation length from the disordered parallel displaced configuration.
  The amount of noise in the correlation function and the lack of an initial peak suggests that 
  the correlation length is less than $\mathit{d}_{equil}$. In general, we see that correlation
  length increases as monomers stack closer together. The same trend has been seen in molecular
  dynamics studies of polymer fluids~\cite{koshy_density_2003}. We hypothesize that the correlation
  length of the sandwiched configuration would increase to a value near experiment if monomers
  packed closer together.

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks at large values of z instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough to create the noise which would 
  cause such behavior. See Section S\ref{S-section:rpi_ft} of the supporting information for
  illustrative examples.

@@

  The simulated intensity of R-$\pi$ is also more intense than experiment because our system
  models near-perfectly straight pores with no defects. Nearly all of the intensity in 
  R-$\pi$ of our simulated patterns is concentrated at a single point. Figure~\ref{fig:simulated_adjusted_colorbar}
  shows the simulated pattern of the ordered sandwiched configuration with the upper boundary
  on the colorbar adjusted to be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only
  distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
  (Figure~\ref{fig:experimental_adjusted_colorbar}, the intensity is more evenly spread out
  over all of R-$\pi$. 
  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
  % out what to do about it
  % BJC5: Could it also be related to noise in xy direction?
  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
  % reflection is arced

@@

>>>>

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{One can only speculate about solute behavior inside the membrane
	  pores based on the previously established picture of the pore structure (a). 
      We use a detailed molecular model in order to appropriately model the pore's
      complex architecture which is crucial to understanding the mechanism of solute
	  transport (b). The head group region is colored blue and the tail region is
	  colored cyan in both representations. This image was generated from the molecular
	  simulations run for this paper.}~\label{fig:detail}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
  systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
  have an equilibrated pore spacing ca. 0.50 nm higher than experiment. Ordered basin systems
  built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.

@@

  \begin{figure}[!htb]
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
  \end{figure}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{box_dimensions.png}
  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5~\AA~$), the unit cell
  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
  constant across all cases. The y dimension box vectors are not included since we use 
  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
  \end{figure}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We extended each simulation by 100 ns in order to get more equilibrated 
  data. We generated simulated patterns using the extended simulation trajectories.
  The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

  % BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
  to sample enough independent configurations. Increasing the number of trajectory frames
  used to simulate the structure factor within a given interval of time does not offer 
  any improvement.

  %BJC5: put figure letters in upper left hand corner of each pattern.
  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			        %\caption{Sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
	        		%\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
	        		%\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			        %\caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
			\end{subfigure}

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
  maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

  The simulated XRD patterns of the parallel displaced configurations show an additional
  reflection due to their helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
  This type of pattern is characteristic of a helix (reference something).
  %BJC5: reference something like a dna diffraction paper
  It is possible that these reflections contribute to the diffuse reflections that connect
  R-spots and R-double in the experimental pattern.

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
  identified spots based on visual inspection. If the spots were not easily discernible, then the 
  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
  lower than experiment in all cases. There is no R-double intensity to be measured. Figures
  are provided in section S\ref{S-section:xrd_intensities} to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type

@@

  \begin{figure}[!htb]
	  \begin{subfigure}{0.45\linewidth}
	  	\centering
	  	\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
	  	\caption{}
	  \end{subfigure}
	  \begin{subfigure}{0.45\linewidth}
	  	\centering
	  	\includegraphics[width=\linewidth]{rzplot_layered_280K_jet.png}
	  	\caption{}\label{fig:sandwiched280K}
	  \end{subfigure}
  \caption{R-spots increases in intensity when the temperature of the system is lowered to 280K.
  In this case, the simulated R-spots is more intense than experiment.}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

  To understand the origin of R-spots, we determined which
  atoms gave rise to the feature. Since R-spots is present as higher intensity
  spots within R-alkanes, it is likely that the spots arise as a consequence of
  the tails. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
  the centroids of the tails (Figure S\ref{S-fig:centroids}) and measured the angle
  between each centroid and its nearest neighbors with respect to the plane of the 
  membrane. We see distinct peaks in the distribution of these angles 
  (Figure~\ref{fig:tail_packing}).

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails}
  are located at $\pm 33 \degree$ which is the same location where the highest
  intensity of spots are located on the simulated patterns. We confirmed this 
  by radially integrating the 2D WAXS pattern for 
  $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe distinct peaks ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figure~\ref{fig:layered_integration}). We performed the same integration on
  the raw experimental data and found the angle at which R-spots reaches its
  highest intensity to be $\pm 37 \degree$ which is a reconcilable difference
  with our simulated results.

@@

  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
	 	\vspace{-2em}
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
        tail-only trajectory still shows R-spots}\label{fig:tails}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{1D correlation functions of the center of masses of aromatic head groups, $g(z)$, show
  decaying oscillatory behavior. We calculated the correlation length by fitting a decaying exponential
  function (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The correlation length is
  longer for ordered basin systems (Table~\ref{table:correlation_length}).
  We did not attempt to calculate the correlation length for (d) because there are no clear peaks. We 
  assume that its correlation is less than the vertical distance between monomers.}\label{fig:correlation}
  \end{figure}

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \midrule
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $\mathit{d}_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
  \bottomrule
  \end{tabular}
  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
  \label{table:correlation_length}
  \end{table}

@@

  The correlation length between stacked monomer head groups of the ordered systems also show
  closer agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
  not extract a reliable correlation length from the disordered parallel displaced configuration
  since the peak heights do not decay significantly. 
  %The amount of noise in the correlation function and the lack of an initial peak suggests that 
  %the correlation length is less than $\mathit{d}_{equil}$.
  In general, we see that correlation length increases as monomers stack closer together. The same
  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
  We hypothesize that the correlation length of the sandwiched configuration would increase to a
  value near experiment if monomers packed closer together.

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough to create the noise which would 
  cause such behavior. See Section S\ref{S-section:rpi_ft} of the supporting information for
  illustrative examples.

@@

  The simulated intensity of R-$\pi$ is also more intense than experiment because our system
  models near-perfectly straight pores with no defects. Nearly all of the intensity in 
  R-$\pi$ of our simulated patterns is concentrated at a single point. Figure~\ref{fig:simulated_adjusted_colorbar}
  shows the simulated pattern of the ordered sandwiched configuration with the upper boundary
  on the colorbar adjusted to be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only
  distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
  over all of R-$\pi$. 
  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
  % out what to do about it
  % BJC5: Could it also be related to noise in xy direction?
  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
  % reflection is arced

@@

  %BJC5: this section may fit better after the next one?
